\documentclass[a4paper,12pt]{article}

\usepackage[utf8]{inputenc}
\usepackage{color,soul}
\usepackage{circledsteps}
\usepackage{ulem}
\usepackage{ragged2e}
\usepackage{blindtext}
\usepackage{nopageno}
\usepackage[LGR,T1]{fontenc}
\usepackage[greek,english]{babel}
\usepackage[absolute]{textpos}
\usepackage{tikz}
\usepackage[paperwidth=5.5in, paperheight=15in, margin=0.7in]{geometry}
\usetikzlibrary{arrows.meta}

\color{blue}
\setulcolor{blue}

\newcommand{\tickitem}{%
    \begin{tikzpicture}[remember picture,overlay]
        \draw[red] (-0.7, 0.1) -- (-0.6, 0) -- (-0.5, 0.5);
    \end{tikzpicture}%
}
\newcommand{\thymusarrows}{%
    \begin{tikzpicture}[remember picture,overlay]
        \draw[->, red] (-1.7, 0.5) -- (-1, 0.3);
		\draw[->, red] (-0.5,1) -- (-0.5, 0.5);
    \end{tikzpicture}%
}
\begin{document}
\begin{center}
Notes \& orig. drafts\\
\end{center}
\begin{flushright} 
\Circled{page 3}\\
\end{flushright}
\begin{center}
\ul{80 Flowers} - 
\setulcolor{red}
\ul{Epigraph} \hfill \color{red} 
\setulcolor{blue}
\ul{b. Dec 25/74}\\
\end{center}
\begin{flushleft}

%arrows from serpyllum and century need to point to thymus
\color{red}
\small
\begin{flushright}
\begin{minipage}[t][2cm]{2.5cm}
variety:\par
T. serpyllum\par
\end{minipage}
\begin{minipage}[t][2cm]{4.5cm}
\raggedleft
\setulcolor{red}
\ul{Century} - common\par
wild thyme Prov. E\par 
thymus \thymusarrows vulgaris sometimes\par
called horse-thyme\par
\end{minipage}
\end{flushright}
\begin{flushleft}
\end{flushleft}
\normalsize
\color{blue}
\begin{itemize}
\renewcommand{\labelitemi}{$\textemdash$}
\item thyme pronounced time


\item tread a measure - "horse for single harness 
uncertain any .. concept(s): 
\sout{firm} will stand firm

\item \tickitem bird(s) tread
\item \tickitem and grows by the {$\stackrel{\hbox{circles the rose}}{\hbox{rose tree(s)}}$} bud fire
\item \tickitem {[the Nine]} \color{red} i.e. heart us invisibly
\color{blue}
\item \tickitem gaping {$\stackrel{\hbox{bot. of}}{\hbox{pod}}$}  flower
\item \tickitem Pall\'adas: {$\stackrel{\hbox{\tiny{ochnay}}}{\hbox{\textgreek{Ὄχνη}}}$} {$\stackrel{\hbox{\tiny{hand, skill of an artist}}}{\hbox{\textgreek{χειρὸς εμὴς}}}$}\\

%check accents for all Greek
{$\stackrel
	{\hbox
		{\tiny
			{sweet}
		}
	}
	{\hbox
		{\textgreek
			{γλυκερὸς
			}
		}
	}
$}
{$\stackrel
	{\hbox
		{\tiny
			{work - hard-work}
		}
	}
	{\hbox
		{\textgreek
		{πόνος
		}
		(ponus)
		}
	}
$}    

sweet 
work hard-work
peartree my handiwork
(grafting the wild pear-tree (pyraster \textgreek{Αχρὰς})
in summer to fruit the upper stem
fragrant-\sout{fruited})
\item \tickitem as happens in 10 yrs
\item \tickitem Nepeta%needs accents
 (\ul{catnip} [corruption of] catmint) 
 {$\stackrel
	{\hbox
		{\tiny
			{mint family ..}
		}
	}
	{\hbox
		{trailing .. gen.}
	}
$} \par
\tickitem aromatic* .. more or less hairy .. stem\sout{s} square\par
\tickitem .. leaves hearth-shaped margins toothed ..\par
\tickitem blue or white flowers, often whorled close\par
\tickitem clusters on stems [(or?) terminal spike] .. corolla 2-lipped, 2-\par
upper, 30lower joined at base, forming\par
narrow tube .. fruit a 20-celled capsule\par
\setulcolor{red}
which ri\ul{pe}ned splits into 4 parts\par
\setulcolor{blue}
L. Nepeta > Etrurian city .. /[?species?] \ul{Nepeta}\par
\tickitem \ul{cataria}, 'tonic \& febrifuge' of Malabar\par
(SW India) coast. Nepenthe(s) epithet\par
\tickitem Egyptian drug > '\ul{ne} \& \ul{penthos} sorrow\par
\tickitem Catnip .. "man's earthly household peace"\par
\tickitem \& \ul{amaranth} '(unwithering)' persi? [persists] Whose\par
\tickitem nature (who's nature)'\par
%page has a few surprising apostrophes etc. I think they might be in red ink, so Z marking as he includes, but hard to say with image quality
\item \tickitem downland - {$\stackrel{\hbox{"loveth not to dance in}}{\hbox{quagmire(s)}}$}%sic unclosed
\item \tickitem sounds invisibly
\item \tickitem \textgreek{ἄρτος}  (Gk. bread) heart us 
%stacking below not quite right. poss better to have artos crossed out then superscript A&C bit
{$\stackrel
	{\hbox
		{\ul
		{A\&C} 
		III xiii 178
		}
	}
	{\hbox
		{\sout
		{artos} 
		}
	}
$} 
\end{itemize}
%down the lh margin
\begin{textblock*}{3.22in}(0.5cm,19cm)%
    \tiny
	\color{blue}
    \begin{minipage}{3.22in} 
		cf \ul{glecoma}\par
		(Gk. mint)\par
		\ul{hederacea}\par
		= ground ivy\par
		or gill-over-\par
		the-ground\par
		or field balm\par
		flowers (clusters)\par
		light to dark\par
		blue\par
  \end{minipage}%
  \end{textblock*}%
  \begin{textblock*}{3.22in}(0.5cm,25.5cm)%
    \tiny
	\color{blue}
	\begin{minipage}{3.22in} 
		\color{red}
		L.
		\color{blue} 
		\tickitem ripa - river\par
		bank, shore,\par
		seashore\par
		cf Plautus  re-\par
		breast\par
		feeding\par
	\end{minipage}%
  \end{textblock*}%


L. th[u]s t[u]s [gk [to thuos]
?incense
frankincense

?from?
?likely? Gk [??]
?? [thus]
mace =
nutmeg
\end{flushleft}
\end{document}

